Tropical wet secondary forest regeneration patterns

### 2021-11-05 analysis/attic/osa.Rmd
filtered NAs in joint cleanData

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F)
#loadpacks
library(tidyverse)
library(BIOMASS)
library(rstatix)
library(ggpubr)
library(ggbeeswarm) #jitter/quasi-random
library(ggpmisc)
library(car)
library(vegan)
#theme
styleOsa <- theme_bw() +
  theme(text = element_text(size = 12))
theme_set(styleOsa)
#import
setwd("~/Documents/u/0/art/res/GitHub/dat/osa")
dat <- read.csv("osa.csv")
```

```{r newTaxa2017}
taxasp <- correctTaxo(genus = dat$gen, 
                      species = dat$sp)  #notneeded

taxa <- getTaxonomy(dat$gen)  #useful
dat$fam <- taxa$family
getWD <- getWoodDensity(genus = dat$gen, 
                        species = dat$sp,
                        family = dat$fam, 
                        stand = dat$plot)
dat$spg <- getWD$meanWD
dat <- subset(dat, dist != "NA")#&gen!="-")#&sp!="sp.")
dat$kg17 <- computeAGB(D = dat$dap, WD = dat$spg, 
                       H = dat$h) * 1000

# both methods do seem equal
```

```{r Chave2014fam, include=F}
attach(dat)
dat$kg14 <- 0.0673 * (spg * dap^2 * h)^0.976

#updatefams
for (name in dat$fam) {
  #if (name == "Bombacaceae" | 
        #name == "Sterculiaceae") {
    #name <- "Malvaceae"
  #}
  #if (name == "Cecropiaceae") {
    #name <- "Urticaceae"
  #}
}
detach(dat)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F)
#loadpacks

library(rstatix)
library(ggpubr)
library(ggbeeswarm) #jitter/quasi-random
library(ggpmisc)
library(car)
library(vegan)
#theme
styleOsa <- theme_bw() +
  theme(text = element_text(size = 12))
theme_set(styleOsa)
